The Host Galaxies of Rapidly Evolving Transients in the Dark Energy Survey

### 2020-03-19 RET_Hosts_IR.tex

\begin{figure*}
\includegraphics[width=\textwidth]{mc_figs/rets_s12_ssfr_corner_final.png}
\caption{\replychris{Corner plot showing the posterior samples from the MCMC fit to the DES RETs and \citet{Sanders2012} sSFRs. Notable features are: 1) the RET distribution is better constrained than the SESNe (S12); 2) the skewness (alpha) for S12 is not well constrained due do the sharp cut off at $-9.5$ (see Fig. \ref{fig:histfit_s12_ssfr}); 3) the RETs scale vs alpha distribution is two-tailed due to alpha being centered close to 0; 4) there is a degeneracy to (3) between RETs loc and alpha for the same reason. Figure produced using the \texttt{corner} package \citep{Foreman-Mackey2016}.}
\label{fig:corner}}
\end{figure*}

>>>>

\begin{figure*}
\includegraphics[width=\textwidth]{mc_figs/rets_s12_ssfr_corner_final.png}
\caption{\replychris{Corner plot showing the posterior samples from the MCMC fit to the DES RETs and \citet{Sanders2012} sSFRs. Notable features are: 1) the RET distribution is better constrained than the SESNe (S12); 2) the scale vs alpha and loc vs scale distributions are two-tailed due to alpha being centred close to 0; 3) there is a degeneracy between loc and alpha for the same reason. Figure produced using the \texttt{corner} package \citep{Foreman-Mackey2016}.}
\label{fig:corner}}
\end{figure*}
